\tool

### 2018-04-03 paper/paper.tex
Pull requests and commits

\section{Tool}
\tool~aims to increase discovery and adoption of useful software engineering tools among developers. This section describes the design and implementation of our system for making recommendations similar to those from a peer and incorporating software engineering industry practices.

\subsection{Peer Interactions}
Previous research shows that recommendations between peers is an effective way to increase tool discovery and adoption~\cite{MurphyHill2011PeerInteraction}. Many existing help systems simulate user-to-user recommendations to increase awareness of application tools and features.

To better understand what makes peer interactions an effective mode of tool discovery, prior work by Brown and colleagues observed how software users recommend tools to each other while completing tasks. They found that \emph{receptiveness} is a significant factor in determining the effectiveness of a tool recommendation while other characteristics, such as politeness and persuasiveness, do not significantly impact recommendation outcome~\cite{vlhcc17}. We designed \tool~to integrate user receptivity into our approach for making tool recommendations to increase awareness of programming tools.

Previous work emphasizes the importance of receptiveness. Fogg outlined best practicies for creating persuasive technology to change user behavior, and argued designers must choose a receptive audience~\cite{FoggPersuasive}. We define receptiveness using two criteria outlined by Fogg: 1) demonstrating desire and 2) familiarity with target behavior. Below we explain how we designed \tool~to recommend programming tools to software developers based on their desire and familiarity.

@@

The primary desire of software users is to have enjoyable and problem-free experiences with software. Developers of these applications also have similar desires, to create high-quality and functioning programs for users. A 2002 study revealed that software engineers demonstrate this desire by spending the majority of the software development process and 70-80\% of their time testing and debugging code~\cite{NIST}. To aid developers in finding, fixing, and preventing various issues in code, many different types of tools have been created to help accomplish these tasks. However, despite the existence of effective tools for detecting errors, the number of bugs in software is increasing~\cite{HaveThingsChanged}. We aim to increase tool discovery by recommending software engineering tools designed to improve software quality.

@@

Choosing an audience familiar with the target behavior is also vital to increasing adoption. To increase use of helpful programming tools, such as static analysis tools, our system focuses on making recommendations to software engineers within the context of the projects they develop. Familiarity with source code is important for creating software applications. Scalabrino and colleagues claim code understandability is one of the most important factors for software development, maintenance, debugging, and testing~\cite{Scalabrino2017Understandability}.

@@

Our system utilizes continuous integration to recommend useful tools before pull request changes are integrated into the main repository, or merged. \tool~is implemented as a plugin for Jenkins, ``the leading open source automation server'' for source code deployment and delivery.\footnote{https://jenkins.io/} The system uses Jenkins to clone Github repositories and periodically check for newly-opened pull requests every 15 minutes. When a new pull request is found, our system uses Jenkins to automatically run our approach to recommend useful software engineering tools.

To analyze the source code, we target projects that use the Maven~\footnote{https://maven.apache.org/} build automation and software management tool for Java applications. Our approach uses Maven to automatically handle dependencies and perform the static analysis when the project builds. We inject the desired software engineering tool as a Maven plugin to repository's \textit{pom.xml} project object model file to add it to the build process. \tool~then builds both the original version of the code before the proposed changes were made (base) and the changed version of the repository with the pull request modifications implemented (head) to inspect differences. Using Maven allows \tool~to run on a large number of Java projects that use the popular build tool and also makes our approach extendable to recommend other tools implemented as Maven plugins in future work.

@@

After analyzing the base and head versions of the code, our approach parses the build output of each version to determine if any reported errors were fixed in the pull request. The software engineering tool identifies faults in the source code, and we take the tool's output and use it in an algorithm we developed to determine if pull request changes fix a reported bug. Our technique uses the code differencing tool GumTree~\cite{GumTree} to identify actions (addition, delete, insert, move, and update) performed between pull request versions and parse the code to convert the text into abstract syntax trees.

@@

%\pseudosubsection{Fix Localizaton}
%TODO: Delete?
%When a fix is identified in the pull request, \tool~then aims to find the location of the fix in the head version. To find the modified line that fixed a bug, we use GumTree to parse the Java file and convert it into abstract syntax trees. We look for the action closest to the offset of the error node calculated from the bug line number reported by the software engineering tool, if applicable. If the closest action is not a delete, then our approach take the location takes the location of that action. Otherwise, if the line was removed our algorithm searches for the closest sibling node or if none exists then the location of the parent. Additionally, the line of the fix had to be converted to the equivalent position in the pull request diff file displaying the changes between file versions, or number of lines below the "@@" header\footnote{https://developer.github.com/v3/pulls/comments/\#create-a-comment}, before moving on to the next phase.

@@

Code reviews from co-workers are often standard practice in software development~\cite{CBirdCodeReviewingTrenches}. Pull requests are the primary method of development contributions and code reviews on Github~\cite{PullRequestReview}. Our approach simulates peer reviews by making recommendations for static analysis tools as a comment to the pull request. \tool~automatically runs software engineering tools and analyzes the code changes, providing feedback to developers based on their changes based on the output from the tool. Github provides functionality for making comments at specific lines of code in a pull request, and \tool~recommends the tool as a comment at the fix location line from the previous step. Figure 1 presents an example recommendation from our system on a pull request. %TODO: Add screenshot

@@

\subsection{Receptiveness}

To choose a familiar audience, our approach makes recommendations on Github pull requests, or proposed code changes submitted by users. Developers should be knowledgeable and familiar with the changes they propose, as well as the code base to which they are contributing. \tool~suggests \textsc{Error Prone} when a reported error is fixed by a developer in a pull request but exists elsewhere in the code.

@@

Our evaluation was limited to Java projects since \textsc{Error Prone} only analyzes Java code. \tool~requires Maven, a build automation and dependency management system for Java projects, to run tools by automatically modifying the Project Object Model (\textit{pom.xml}) configuration file and building projects. We chose the most forked and starred repositories to study the most popular projects on GitHub. We target projects that don't use \textsc{Error Prone} to increase awareness for developers who are not knowledgeable about the tool. Stars are a social aspect of GitHub where users can indicate favorite projects and repositories of interest\footnote{https://help.github.com/articles/about-stars/}. GitHub suggests forking repositories as a best practice for making contributions and pull requests to projects\footnote{https://help.github.com/articles/fork-a-repo/}.

After compiling a list of repositories that met the above criteria, we selected the top 250 projects based on the creation date of their last 10 pull requests. We chose projects with more recent pull requests to provide more opportunities for \tool~to make recommendations. The evaluation repositories include a wide range of software applications with diversified functions and created by many different companies and developers. A list of projects used for this study is publicly available online.\footnote{\url{https://gist.github.com/tool-recommender-bot/1769ccd148508beabcd273a731723860}}
%TODO: Maybe examples of projects?

@@

To answer our first research question, we observed how often our approach makes recommendations on newly opened pull requests. In addition to the frequency of recommendations, we also tracked instances where \textsc{Error Prone} defects were removed but not reported as fixed according to our fix identification algorithm in Section III.B.2, the number of occurrences where errors were fixed but no other instances of that bug were found in the code, and the false positive rate.

Johnson and colleagues discovered one of the primary barriers to static analysis tool usage among software engineers is false positives in the output~\cite{Johnson2013Why}. To prevent unnecessary recommendations from our system, we manually reviewed all instances where \tool~reported a recommendation should be made. After inspecting each reported pull request, we determined whether it was an appropriate case for our system to make a recommendation to developers. If so, we proceeded to post the comment recommending \textsc{Error Prone} on the pull request. Otherwise, we noted the instance of a false positive in our approach and did not make a recommendation.

@@

To gather data on the usefulness of our system, we sent a follow-up survey to developers. Survey participants were users who received a recommendation from \tool~on their pull request. We asked developers about their awareness of \textsc{Error Prone} and how likely they are to use the tool in the future. The survey also included a free-response section to provide an opportunity for participants to add comments on the usefulness of the recommendation.

@@

Effective tool recommendation systems should have ample opportunities to regularly make recommendations to users. To determine how often \tool~automatically recommends \textsc{Error Prone}, we observed the number of pull request comments made by our tool. Our evaluation lasted for [some period of time], and we calculated the amount of true positive recommendations during that time span to measure the recommendation rate for each GitHub repository used in our study. To calculate the false positive rate, we compared the number of unnecessary instances where our tool proposed a recommendation found by researchers to the total number of instances where a recommendation reported by \tool.

>>>>

\section{Tool}
\tool~aims to increase discovery and adoption of useful software engineering tools among developers. This section describes the design and implementation of our approach.

\subsection{Peer Interactions}
Previous research shows that recommendations between colleagues is the most effective way to increase tool discovery and adoption~\cite{MurphyHill2011PeerInteraction}. Murphy-Hill interviewed software engineers and found that user-to-user peer interactions occur less frequently but are much more effective that system-to-user solutions.~\cite{MurphyHill2011PeerInteraction}~\cite{Murphy-Hill2015HowDoUsers}.

To better understand what makes peer interactions an effective mode of tool discovery, prior work by Brown and colleagues observed how software users recommend tools to each other while completing tasks. They found that \emph{receptiveness} is a significant factor in determining the effectiveness of a tool recommendation, while other characteristics such as politeness and persuasiveness do not significantly impact the outcome of a suggestion~\cite{vlhcc17}. We designed \tool~to integrate user receptivity into our approach for making tool recommendations to increase awareness of programming tools.

Previous work emphasizes the importance of user receptiveness. Fogg outlined best practicies for creating persuasive technology to change user behavior, and argued designers must choose a receptive audience~\cite{FoggPersuasive}. We define receptiveness using two criteria outlined by Fogg: 1) demonstrating desire and 2) familiarity with target behavior. Below we explain how we designed \tool~to recommend programming tools to software developers based on their desire and familiarity.

@@

The primary desire of software users is to have enjoyable and problem-free experiences with software. Developers of these applications also have similar desires, to create high-quality and functioning programs for users. A 2002 study revealed that software engineers demonstrate this desire by spending the majority of the software development process and 70-80\% of their time testing and debugging code~\cite{NIST}. To aid developers in finding, fixing, and preventing various issues in code, many different types of tools have been created to help accomplish these tasks. However, despite the existence of effective tools for detecting errors, the number of bugs in software is increasing~\cite{HaveThingsChanged}. \tool~aims to increase tool discovery by recommending software engineering tools designed to promote developers' desires for improving software quality.

@@

Choosing an audience familiar with the target behavior is also vital to increasing adoption. To increase use of helpful programming tools, our system focuses on making recommendations to software engineers within the context of the projects they develop. Scalabrino and colleagues claim code understandability is one of the most important factors for software development, maintenance, debugging, and testing~\cite{Scalabrino2017Understandability}. \tool~uses familiarity with source code to recommend tools to software engineers in code they modify.

To choose a familiar audience, our approach makes recommendations on proposed Github code changes submitted by users. Developers should be knowledgeable and familiar with the changes they propose, as well as the code base to which they are contributing. \tool~suggests \textsc{Error Prone} when a reported error is fixed by a developer in a pull request or commit, and the same bug exists elsewhere in the code.

@@

Our system utilizes continuous integration to recommend useful tools beforecode changes are integrated into the main repository, or merged. \tool~is implemented as a plugin for Jenkins, ``the leading open source automation server'' for source code deployment and delivery.\footnote{https://jenkins.io/} The system uses Jenkins to clone Github repositories and periodically check for newly-opened pull requests and commits every 15 minutes. When a new code change is found, our system uses Jenkins to automatically run our approach to recommend useful software engineering tools.

To analyze the source code, we target projects that use the Maven~\footnote{https://maven.apache.org/} build automation and software management tool for Java applications. Our approach uses Maven to automatically handle dependencies and perform the static analysis when the project builds. We inject the desired software engineering tool as a Maven plugin to repository's \textit{pom.xml} project object model file to add it to the build process. \tool~then builds both the original version of the code before the proposed changes were made (base) and the changed version of the repository with the modifications implemented (head) to inspect differences. Using Maven allows \tool~to run on a large number of Java projects that use the popular build tool and also makes our approach extendable to recommend other tools implemented as Maven plugins in future work.

@@

After analyzing the base and head versions of the code, our approach parses the build output of each version to determine if any reported errors were fixed in the code modifications. The software engineering tool identifies faults in the source code, and we take the tool's output and use it in an algorithm we developed to determine if GitHub user code changes fix a reported bug. Our technique uses the code differencing tool GumTree~\cite{GumTree} to identify actions (addition, delete, insert, move, and update) performed between altered code versions and parse the source code to convert the text into abstract syntax trees.

@@

%\pseudosubsection{Fix Localizaton}
%TODO: Delete?
%When a fix is identified in the changed version of code, \tool~then aims to find the location of the fix in the head version. To find the modified line that fixed a bug, we use GumTree to parse the Java file and convert it into abstract syntax trees. We look for the action closest to the offset of the error node calculated from the bug line number reported by the software engineering tool, if applicable. If the closest action is not a delete, then our approach take the location takes the location of that action. Otherwise, if the line was removed our algorithm searches for the closest sibling node or if none exists then the location of the parent. Additionally, the line of the fix had to be converted to the equivalent position in the pull request or commit diff file displaying the changes between file versions, or number of lines below the "@@" header\footnote{https://developer.github.com/v3/pulls/comments/\#create-a-comment}, before moving on to the next phase.

@@

Code reviews from co-workers are often standard practice in software development~\cite{CBirdCodeReviewingTrenches}. Pull requests and commits are the primary methods of development contributions and code updates on GitHub~\cite{PullRequestReview}. Our approach simulates peer reviews by making recommendations for static analysis tools as a comment to the pull request or commit. \tool~automatically runs software engineering tools and analyzes the code changes, providing feedback to developers based on their changes based on the output from the tool. Github allows users to make comments on specific lines of code changed in pull requests and commits. \tool~leverages this functionality by recommending the tool as a comment at the fix location line from the previous step. Figure 1 presents an example recommendation from our system on a pull request. %TODO: Add screenshot

@@

@@

Our evaluation was limited to Java projects since \textsc{Error Prone} only analyzes Java code. \tool~requires Maven, a build automation and dependency management system for Java projects, to run tools by automatically modifying the Project Object Model (\textit{pom.xml}) configuration file and building projects. We chose the most forked and starred repositories to study the most popular projects on GitHub. We target projects that don't use \textsc{Error Prone} to increase awareness for developers who are not knowledgeable about the tool. Stars are a social aspect of GitHub where users can indicate favorite projects and repositories of interest\footnote{https://help.github.com/articles/about-stars/}.

After using a GitHub search API to find projects that met the above criteria, we compiled a list of 789 code repositories. The evaluation projects include a wide range of software applications with diversified functions and created by many different companies and developers. A list of projects used for this study is publicly available online.\footnote{\url{https://gist.github.com/tool-recommender-bot/1769ccd148508beabcd273a731723860}}
%TODO: Maybe examples of projects?

@@

To answer our first research question, we observed how often our approach makes recommendations on commits and pull requests. In addition to the frequency of recommendations, we also tracked instances where \textsc{Error Prone} defects were removed but not reported as fixed according to our fix identification algorithm in Section III.B.2, the number of occurrences where errors were fixed but no other instances of that bug were found in the code, and the false positive rate.

Johnson and colleagues discovered one of the primary barriers to static analysis tool usage among software engineers is false positives in the output~\cite{Johnson2013Why}. To prevent unnecessary recommendations from our system, we manually reviewed all instances where \tool~reported a recommendation should be made. After inspecting each repository modification, \tool~determined whether it was an appropriate case to make a recommendation to the developer. If so, we proceeded to post the comment recommending \textsc{Error Prone} on the code change. Otherwise, we noted the instance of a false positive in our approach and did not make a recommendation.

@@

To gather data on the usefulness of our system, we sent a follow-up survey to developers. Survey participants were users who received a recommendation from \tool~on their pull request or commit. We asked developers about their awareness of \textsc{Error Prone} and how likely they are to use the tool in the future. The survey also included a free-response section to provide an opportunity for participants to add comments on the usefulness of the recommendation.

@@

Effective tool recommendation systems should have ample opportunities to regularly make recommendations to users. To determine how often \tool~automatically recommends \textsc{Error Prone}, we observed the number of recommendation comments made by our tool. Our evaluation lasted for [some period of time], and we calculated the amount of true positive recommendations during that time span to measure the recommendation rate for each GitHub repository used in our study. To calculate the false positive rate, we compared the number of unnecessary instances where our tool proposed a recommendation found by researchers to the total number of instances where a recommendation reported by \tool.
